---
title: "Contamination Report"
output: html_document
---

## Contamination Overview Plots

```{r echo=FALSE, warning=FALSE, message=FALSE, fig.width=12, fig.height=10}
list.of.packages <- c("ggplot2", "knitr", "stringr", "readr", "data.table")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(readr))
suppressPackageStartupMessages(library(data.table))

args <- commandArgs(trailingOnly = TRUE)

args <- commandArgs(trailingOnly = TRUE)
contam = read.table(args[1], header = TRUE, sep="\t");
meta<-data.frame(with(contam, table(Contamination)))
```
---

## Graphical overview 

```{r echo=FALSE, fig.width=5.5, fig.height=4, result='asis'}

print(ggplot(data=meta, aes(x=Contamination, y=Freq, fill=Contamination)) + geom_bar(stat="identity") + xlab("Contamination Status") + ylab("Samples")  )

```
---

## Verdict 


This interactive table shows the detected contaminated samples. 

```{r echo=FALSE, results='asis'}
if(nrow(contam)>0){
	
	kable(contam[,c(1,2,3,4,5,6,7,8,9,10)], "html", table.attr = "id=\"contam_table\" class=\"table table-bordered table-striped display responsive nowrap\"",caption = "") 

} else{

	cat("<div class='alert alert-neutral'>No entries found!</div>")
	
}
```
<script type="text/javascript">
  $(document).ready(function() {
  	$('#contam_table').DataTable({
  	
       responsive: {
            details: {
                display: $.fn.dataTable.Responsive.display.modal( {
                    header: function ( row ) {
                        var data = row.data();
                        return 'Details for '+data[0];
                    }
                } ),
                renderer: function ( api, rowIdx, columns ) {
                    var data = $.map( columns, function ( col, i ) {
                        return '<b>' + col.title+':'+'</b><br>'+
                                col.data+'<br><hr>';
                    } ).join('');
 
                    return $('<div/>').append( data );
                }
            }
       },
         
       "fnRowCallback": function( nRow, aData, iDisplayIndex, iDisplayIndexFull ) {
          if ( aData[6] != "1" ){
            $('td', nRow).css('background-color', '#f2dede');
          }
       }
  	
  	});
	} );
</script>

